---
title: "Homework 6: Data Manipulation"
author: "Your Name"
date: "March 4, 2024"
output: html_document
---

The Gapminder project's mission is to fight devastating ignorance with a fact-based worldview everyone can understand. To do this, they assemble reliable data about a variety of global variables to help educate the general public.

I have collected data from Gapminder about several variables: 

- Population
- GDP Per Capita (inflation-adjusted US dollars)
- Mean Household Income
- CO2 emissions (tonnes per capita)
- Energy Use (Kg of Oil-equivalent per capita)

Use the data manipulation tools you've learned about to answer each of the following questions, which I've grouped into several general topics. Some questions may specify a specific language to use; if no language is specified, you may choose whether to use R or python to answer the question.

## Read In the Data

Read in the data in R and Python. In both languages, store the table in the variable `gapminder`. 

```{r, include = F}

```

```{python}

```



## Data Exploration

### Missingness

Gapminder puts a lot of effort into curating certain variables; other variables are less frequently used (or are harder to assemble from reliable sources). 

#### CO2
Create a table of all countries with at least 30 observations of the CO2 variable. Your table should be called `co2_sum` and should have columns `country` and `n_obs`. Do not print out the table; instead, if you have done everything correctly, when your document is compiled the correct number of countries will be filled in in the sentence below the code chunk.

<!-- Use R -->
```{r, echo = T}
co2_sum <- data.frame() # This is a blank data frame so that the lines below 
                        # work before you've filled your code in.
                        # You can write your code below this line, or remove 
                        # these lines, whichever you prefer.

```

There are `r nrow(co2_sum)` countries with at least 30 years of CO2 data. On average, countries have `r mean(co2_sum$n_obs)` years of data.

#### Energy

For each country with defined energy data for at least 10 years, summarize the data by computing the following:



- year of minimum energy consumption per capita
- year of maximum energy consumption per capita
- average rate of energy consumption change from min to max.    
A rough estimate might be something like (max consumption - min consumption)/(max year - min year). This may not include the most recent data; that is ok.

Your summary data frame, `energy_sum` should have one row for each country, with columns `yearmin`, `yearmax`, and `avgincrease`.

Answer in Python

```{python}

```


#### Income

Locate the country which has had the biggest growth in income between 1980 and 2019. Create a simple line graph or scatter plot showing the income in this country (and only this country) over time.

#### GDP

Locate the country which had the biggest decrease (or smallest increase, if there are no decreases) in GDP between 1990 and 2022. Include only countries with at least 5 years of reported data between 1990 and 2022. Create a simple line graph or scatter plot showing the GDP in this country for all years which this information is provided.
