---
title: "Homework 6: Data Manipulation"
author: "Your Name"
date: "March 4, 2024"
output: html_document
---

```{r}
co2_sum <- data.frame() # This is here to be a blank data frame so that the 
                        # lines below work before you've filled your code in.
```

The Gapminder project's mission is to fight devastating ignorance with a fact-based worldview everyone can understand. To do this, they assemble reliable data about a variety of global variables to help educate the general public.

I have collected data from Gapminder about several variables: 

- Population
- GDP Per Capita (inflation-adjusted US dollars)
- Mean Household Income
- CO2 emissions (tonnes per capita)
- Energy Use (Kg of Oil-equivalent per capita)

Use the data manipulation tools you've learned about to answer each of the following questions, which I've grouped into several general topics. Some questions may specify a specific language to use; if no language is specified, you may choose whether to use R or python to answer the question.

## Read In the Data

Read in the data in R and Python. In both languages, store the table in the variable `gapminder`. 

```{r, include = F}

```

```{python}

```



## Data Exploration

### Missingness

Gapminder puts a lot of effort into curating certain variables; other variables are less frequently used (or are harder to assemble from reliable sources). 

#### CO2
Create a table of all countries with at least 30 observations CO2. Your table should be called `co2_sum` and should have columns `country` and `n_obs`. Do not print out the table; instead, if you have done everything correctly, when your document is compiled the correct number of countries will be filled in in the sentence below the code chunk.

<!-- Use R -->
```{r, echo = T}

```

There are `r nrow(co2_sum)` countries with at least 30 years of CO2 data.

#### Energy
Answer in Python

```{python}

```


#### Income

#### GDP

